\documentclass[10pt, twoside, ebook]{memoir}

\input{preamble}
\input{glossary}

\begin{document}

\begin{titlingpage}
  \input{front_cover}
\end{titlingpage}

\aliaspagestyle{title}{empty} % Suppress page number in title
\maketitle

\clearpage
\thispagestyle{empty}
\null\vfill
\begin{flushleft}
  Copyright © 2021 Michael You. All rights reserved.
  \bigskip

  No part of this publication may be reproduced, transmitted in any form or by any
  means, electronic, mechanical, photocopying, recording, scanning, or otherwise,
  except as permitted under Section 107 or 108 of the 1976 United States Copyright
  Act, without either the prior written permission of the Author. To request
  permissions, please contact
  \href{mailto:viridity.capital@gmail.com}{\te{viridity.capital@gmail.com}}.
  \bigskip

  Limit of Liability/Disclaimer of Warranty. While the author have used their best
  efforts in preparing this book, the methods and exercises prescribed in this
  book make no representations or warranties with respect to accuracy or
  effectiveness. The advice and strategies contained herein may not be suitable
  for your situation, and may work with limited success. You should consult with a
  professional where appropriate. The author will not be liable for any
  relationship damage, bodily harm, or any other damages.
  \bigskip
\end{flushleft}

\frontmatter
\tableofcontents*

\input{forward}

\mainmatter
\include{chapters/number_sense}

\appendix
\include{appendix}

\backmatter
\bibliographystyle{plain}
\bibliography{biblio}

\printglossaries

\printindex

\cleartoverso
\include{back_cover}
\end{document}